"
***************************************************************************
Sampling_PSSP_to_R.Rmd
---------------------
Date                 : December 2019
Copyright            : (C) 2019 by Felipe Carranza
Email                : fcarranza@protonmail.com
***************************************************************************
*                                                                         *
*   This program is free software; you can redistribute it and/or modify  *
*   it under the terms of the MIT  License *
*                                                                         *
*                                                                         *
***************************************************************************

__author__ = 'Felipe Carranza'
__date__ = 'December 2019'
__copyright__ = '(C) 2019, Felipe Carranza'
"


---
title: "jovenes_formación_laboral_PSPP on R from PSPP"
author: "Felipe Carranza from PSPP guide from Master William Lázaro"
date: "DIc  2019"
output:
  html_document:
    df_print: paged
    theme: paper
  html_notebook: null
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**Estratified Sampling**
\vspace{12pt}
** It is desired to make a study to define the level of labor insertion that young people have to attend the Enabling for Work (SKILL) courses. Knowing that a pilot study indicates that the insertion level is 15%, determine the required sample size of young people for a confidence level of 98%, assuming a margin of error of 4% **

```{r}
#Directory .sav
setwd("~/Descargas")
#library from read .sva files
library(foreign)
#LReading file by : ";"
dataset=read.spss("bd jovenes con formacion laboral.sav",to.data.frame = TRUE)
str(dataset)
#Tble frecuency html library
library(table1)

#Exploring frecuency by department, sex, education level

table1(~    dataset$DEPTO_RESIDENCIA | dataset$sexo  + dataset$NIVEL_ACADEMICO, data=dataset)


#Exploring frecuency by department, sex
table1(~    dataset$NIVEL_ACADEMICO   | dataset$sexo , data=dataset)

#Ordenar by level education and sex

#Factor variables

dataset$refactor_edu <- factor(dataset$NIVEL_ACADEMICO,
                   labels = c(1,2,3,4,5,6,7),
                   levels =c("1°/3° GRADO", "4°/6° GRADO", "7°/9° GRADO", "BACHILLERATO ", "NINGUNO      ","TECNOLOGICO  ","UNIVERSITARIO"))

#Showing by category
(table(dataset$refactor_edu))

#Grouping category 1 tp2 y to 5
dataset$refactor_edu[dataset$refactor_edu==2 |dataset$refactor_edu==5 ]=1

#Showing by category
(table(dataset$refactor_edu))

#Creting new factor label 1: "Menor de sexto grado"
dataset$refactor_edu2 <- factor(dataset$refactor_edu,
                           levels = c(1,3,4,6,7),
                           labels =c("Menor 6° GRADO",  "7°/9° GRADO", "BACHILLERATO ", "TECNOLOGICO  ","UNIVERSITARIO")
                           )

#Showing by category
(table(dataset$refactor_edu2))
#Ordering  Datase by level education and sex
dataset=dataset[order(dataset$NIVEL_ACADEMICO,dataset$sexo), ]

#Selecting Estrate, error 0.04, confidenc: 98%
Estrato1 = dataset[dataset$refactor_edu==1,]  #P = 0.05  Sample size afijation 28
Estrato2 = dataset[dataset$refactor_edu==3,]  #P = 0.150 Sample size afijation 108
Estrato3 = dataset[dataset$refactor_edu==4,]  #P = 0.200 Sample size afijation 310
Estrato4 = dataset[dataset$refactor_edu==6,]  #P = 0.300 Sample size afijation 15
Estrato5 = dataset[dataset$refactor_edu==7,]  #P = 0.350 Sample size afijation 45


#Selectin random samping into of each estrate
#Creating the samples
Muestra_Estrato1 =Estrato1[sample(dim(Estrato1)[1],28,replace=FALSE),]
#saving
write.csv(Muestra_Estrato1, file = "Muestra_Estrato1.csv")
#dims
dim(Muestra_Estrato1)

Muestra_Estrato2=Estrato2[sample(dim(Estrato2)[1],108,replace=FALSE),]
#Creating the samples
write.csv(Muestra_Estrato2, file = "Muestra_Estrato2.csv")
#dims
dim(Muestra_Estrato2)

Muestra_Estrato3 =Estrato3[sample(dim(Estrato3)[1],310,replace=FALSE),]
#Creating the samples
write.csv(Muestra_Estrato3, file = "Muestra_Estrato3.csv")
#dims
dim(Muestra_Estrato3)

Muestra_Estrato4 =Estrato4[sample(dim(Estrato4)[1],15,replace=FALSE),]
#Creating the samples
write.csv(Muestra_Estrato4, file = "Muestra_Estrato4.csv")
#dims
dim(Muestra_Estrato4)

Muestra_Estrato5 =Estrato5[sample(dim(Estrato5)[1],45,replace=FALSE),]
#Creating the samples
write.csv(Muestra_Estrato5, file = "Muestra_Estrato5.csv")
#dims
dim(Muestra_Estrato5)

                   

```
